---
title: "Scraping"
author: "Brett Graham & Gunnar Goeden"
date: "11/8/2017"
output: html_document
---

### Notes:
Need NFL game score data as follows:\
week number, home/away teams, scores, rushing yards, rushing attempts, rushing td, rushing fumbles, passing yards, passing TD, passing attempts, passing completions.

```{r}
library(xml2)
library(rvest)
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
```


https://www.rstudio.com/wp-content/uploads/2015/02/data-wrangling-cheatsheet.pdf

#Questions:
How to split numeric values scraped as "x-y-z" ?
How to incorporate week into data table? (ie. How to say "all dates from 9/10/15 to 9/14/15 = week 1")

##2015 Team & Score Data (first webpage)
```{r}
url2015 <- 'http://www.footballdb.com/games/index.html?lg=NFL&yr=2015'
webpage2015 <- read_html(url2015)

date15_html <- html_nodes(webpage2015,'td:nth-child(1) .hidden-xs')
date15_data <- html_text(date15_html)

visitteam15_html <- html_nodes(webpage2015,'td:nth-child(2) .hidden-xs')
visitteam15_data <- html_text(visitteam15_html)

visitscore15_html <- html_nodes(webpage2015,'#leftcol .center:nth-child(3)')
visitscore15_data <- html_text(visitscore15_html)
visitscore15_data <-as.numeric(visitscore15_data)

hometeam15_html <- html_nodes(webpage2015,'.center+ td > .hidden-xs')
hometeam15_data <- html_text(hometeam15_html)

homescore15_html <- html_nodes(webpage2015,'.center:nth-child(5)')
homescore15_data <- html_text(homescore15_html)
homescore15_data <-as.numeric(homescore15_data)

fbscores2015 <- data.frame(Date = date15_data, Visiting_Team = visitteam15_data, Visiting_Score = visitscore15_data, Home_Team = hometeam15_data, Home_Score = homescore15_data)
#fbscores2015
```

##2016 Team & Score Data 
```{r}
url2016 <- 'http://www.footballdb.com/games/index.html?lg=NFL&yr=2016'
webpage2016 <- read_html(url2016)

date16_html <- html_nodes(webpage2016,'td:nth-child(1) .hidden-xs')
date16_data <- html_text(date16_html)

visitteam16_html <- html_nodes(webpage2016,'td:nth-child(2) .hidden-xs')
visitteam16_data <- html_text(visitteam16_html)

visitscore16_html <- html_nodes(webpage2016,'#leftcol .center:nth-child(3)')
visitscore16_data <- html_text(visitscore16_html)
visitscore16_data <-as.numeric(visitscore16_data)

hometeam16_html <- html_nodes(webpage2016,'.center+ td > .hidden-xs')
hometeam16_data <- html_text(hometeam16_html)

homescore16_html <- html_nodes(webpage2016,'.center:nth-child(5)')
homescore16_data <- html_text(homescore16_html)
homescore16_data <-as.numeric(homescore16_data)

fbscores2016 <- data.frame(Date = date16_data, Visiting_Team = visitteam16_data, Visiting_Score = visitscore16_data, Home_Team = hometeam16_data, Home_Score = homescore16_data)
#fbscores2016
```

##2017 Team & Score Data 
```{r}
url2017 <- 'http://www.footballdb.com/games/index.html?lg=NFL&yr=2017'
webpage2017 <- read_html(url2017)

date17_html <- html_nodes(webpage2017,'td:nth-child(1) .hidden-xs')
date17_data <- html_text(date17_html)
date17_data <- as.Date(date17_data,"%m/%d/%Y")

visitteam17_html <- html_nodes(webpage2017,'td:nth-child(2) .hidden-xs')
visitteam17_data <- html_text(visitteam17_html)

visitscore17_html <- html_nodes(webpage2017,'#leftcol .center:nth-child(3)')
visitscore17_data <- html_text(visitscore17_html)
visitscore17_data <-as.numeric(visitscore17_data)

hometeam17_html <- html_nodes(webpage2017,'.center+ td > .hidden-xs')
hometeam17_data <- html_text(hometeam17_html)

homescore17_html <- html_nodes(webpage2017,'.center:nth-child(5)')
homescore17_data <- html_text(homescore17_html)
homescore17_data <-as.numeric(homescore17_data)

fbscores2017 <- data.frame(Date = date17_data, Visiting_Team = visitteam17_data, Visiting_Score = visitscore17_data, Home_Team = hometeam17_data, Home_Score = homescore17_data)
#fbscores2017
```

```{r}
date_html <- html_nodes(webpage2017,'td:nth-child(1) .hidden-xs , .divheader')
date_data <- html_text(date_html)
#date_data

week <- rep(0,256)
if (date17_data >= "2017-09-14") week=1 else week=0
mutate(fbscores2017, Week=week)

#date17_data
#week <- rep(0,50)

```


```{r}
url <- "http://www.footballdb.com/games/boxscore.html?gid=2017091001"

#Reading the HTML code from the website
webpage <- read_html(url)

title_data_html <- html_nodes(webpage,"#divBox_team tbody .left")
title_data <- html_text(title_data_html)
title_data <- append(c("Team", "Points"), title_data)

# #Create boxscore 
# boxscore <- data.frame(Category = title_data, Home = home_data, Away = away_data)

#Create game event (single row that describes game)
home_variables <- paste0(rep("Home_",length(title_data)),title_data)
away_variables <- paste0(rep("Away_",length(title_data)),title_data)
event_variables <- append(home_variables,away_variables)
event_variables <- append(c("Date","Week"),event_variables)

length(event_variables)

```

```{r}
createDateVector <- function(year){
  url <- paste0('http://www.footballdb.com/games/index.html?lg=NFL&yr=',toString(year))
  webpage <- read_html(url)
  date_html <- html_nodes(webpage,'td:nth-child(1) .hidden-xs')
  date_data <- html_text(date_html)
  dateVect <- as.Date(date_data,"%m/%d/%Y")
  
  today = today()
  daysBeforeToday = dateVect <= today
  dateVect = dateVect[daysBeforeToday]
}
```

```{r}
dateToURL <- function(dateVect, i, adjustment=0){
  url_base <- 'http://www.footballdb.com/games/boxscore.html?gid='
  url_year = year(dateVect[i])
  if(month(dateVect[i])<10){
    url_month <- paste0("0",month(dateVect[i]))
  }else{
    (url_month <-toString(month(dateVect[i])))
   }
  if(day(dateVect[i])<10){
    url_day <- paste0("0",day(dateVect[i]))
  }else{
    url_day <-toString(day(dateVect[i]))
  }
  
  gameNum = 1
  location = i-1
  if(location >0){
    while(dateVect[i]==dateVect[location]){
      gameNum = gameNum+1
      location=location-1
      
      if(location==0){
        break
      }
    }
  }
  
  gameNum = gameNum + adjustment
  
  if(gameNum<10){
    url_gamenum <- paste0("0",toString(gameNum))
  }else{
    url_gamenum <-toString(gameNum)
  }

  url <- paste0(url_base,url_year,url_month,url_day,toString(url_gamenum))

  
  return(list(url=url,url_year=url_year,url_month = url_month,url_day=url_day))
}
```
```{r}
yearlyStats <- function(dateVect){
  data = matrix(rep('',length(event_variables)),nrow=1)
  
  for(i in 1:length(dateVect)){


    url_info <- dateToURL(dateVect,i)
    url <- url_info$url
    
    webpage <- read_html(url)
  
  
    away_data_html <- html_nodes(webpage,'#divBox_team .row1 .left+ td , .section_left .left+ td .hidden-xs , #divBox_team .row0 .left+ td')
    away_data <- html_text(away_data_html)
    away_points <- html_text(html_nodes(webpage,'#leftcol .header+ .center td+ td b'))
    away_data <- append(away_data,away_points, after = 1)
  
    home_data_html <- html_nodes(webpage,"#divBox_team .row1 .left~ td+ td , #divBox_team .row0 .left~ td+ td , .section_left .left~ td+ td .hidden-xs")
    home_data <- html_text(home_data_html)
    home_points <- html_text(html_nodes(webpage,'#leftcol .row0+ .center td+ td b'))
    home_data <- append(home_data,home_points, after = 1)
    
    week_info <- html_text(html_nodes(webpage,'#breadcrumbs a~ a+ a'))
  
    date = paste0(url_info$url_month,"/",url_info$url_day,"/",url_info$url_year)
    date = append(date,week_info)
    game_data = append(date,home_data)
    game_data = append(game_data,away_data)
    
    
    
    adjustment = 1
    while(length(game_data)==2 |length(game_data)==1){
      url <- dateToURL(dateVect,i,adjustment = adjustment)$url
    
      webpage <- read_html(url)
    
      away_data_html <- html_nodes(webpage,'#divBox_team .row1 .left+ td , .section_left .left+ td .hidden-xs , #divBox_team .row0 .left+ td')
      away_data <- html_text(away_data_html)
      away_points <- html_text(html_nodes(webpage,'#leftcol .header+ .center td+ td b'))
      away_data <- append(away_data,away_points, after = 1)
    
      home_data_html <- html_nodes(webpage,"#divBox_team .row1 .left~ td+ td , #divBox_team .row0 .left~ td+ td , .section_left .left~ td+ td .hidden-xs")
      home_data <- html_text(home_data_html)
      home_points <- html_text(html_nodes(webpage,'#leftcol .row0+ .center td+ td b'))
      home_data <- append(home_data,home_points, after = 1)
      
      week_info <- html_text(html_nodes(webpage,'#breadcrumbs a~ a+ a'))

    
      date = paste0(url_info$url_month,"/",url_info$url_day,"/",url_info$url_year)
      date = append(date,week_info)
      game_data = append(date,home_data)
      game_data = append(game_data,away_data)
    
      adjustment = adjustment+1
    
    
      if(adjustment >100){
        print("ERROR: ADJUSTMENT TOO LARGE")
        print(i)
        break
      }
  
    }
    data = rbind(data,game_data)
  
  }
  return(data)
}
```
```{r}
createDataframe <- function(year){
  dateVect = createDateVector(year)
  data_mat = yearlyStats(dateVect)
  data_mat = data_mat[-1,]
  game_stats <- data.frame(data_mat)
  names(game_stats)[1:length(event_variables)] <- event_variables
  names(game_stats)[c(12,40)] <- c('Home_Avg Rush Gain','Away_Avg Rush Gain')
  return(game_stats)
    
}
```
```{r}
createPredictionsDataFrame <- function(year){
  url <- paste0('http://www.footballdb.com/games/index.html?lg=NFL&yr=',year)
  webpage <- read_html(url)
  
  date_html <- html_nodes(webpage,'td:nth-child(1) .hidden-xs')
  date_data <- html_text(date_html)
  date_data <- as.Date(date_data,"%m/%d/%Y")
  
  visitteam_html <- html_nodes(webpage,'td:nth-child(2) .hidden-xs')
  visitteam_data <- html_text(visitteam_html)
  
  visitscore_html <- html_nodes(webpage,'#leftcol .center:nth-child(3)')
  visitscore_data <- html_text(visitscore_html)
  visitscore_data <-as.numeric(visitscore_data)
  
  hometeam_html <- html_nodes(webpage,'.center+ td > .hidden-xs')
  hometeam_data <- html_text(hometeam_html)
  
  homescore_html <- html_nodes(webpage,'.center:nth-child(5)')
  homescore_data <- html_text(homescore_html)
  homescore_data <-as.numeric(homescore_data)
  
  fbscores <- data.frame(Date = date_data, Home_Team = hometeam17_data, Home_Points = homescore17_data, Away_Team = visitteam17_data, Away_Points = visitscore17_data)
  
  return(fbscores)
  
}

# View(createPredictionsDataFrame(2017))



```


```{r}
# game_stats_2010 <- createDataframe(2010)
# game_stats_2010<- game_stats_2010[-c(208,240),]
# game_stats_2011 <- createDataframe(2011)
# game_stats_2012 <- createDataframe(2012)
# game_stats_2013 <- createDataframe(2013)
# game_stats_2014 <- createDataframe(2014)
# game_stats_2014<- game_stats_2014[-176,]
# game_stats_2015 <- createDataframe(2015)
# game_stats_2016 <- createDataframe(2016)
game_stats_2017 <- createDataframe(2017)
game_stats_2017 <- game_stats_2017[-159,]


View(game_stats_2017)
```






