---
title: "Brett rjags"
author: "Brett Graham"
date: "12/6/2017"
output: html_document
---

```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(readr)
library(igraph)
library(rjags)
set.seed(1000)
```
##Model skeleton for Offensive & Defensive rank to predict score. (Hierarchical structure to draw average of team from average of league?)

```{r}
#Overspecified Model where offensive stats combine into an offensive score and likewise with defenseive stats


modelData <- filter(modelDF2016,Week>5)

main1 <- "model{
  #Data 
  for(i in 1:length(y)) {
      y[i] ~ dpois(rate[i])
      rate[i] ~ dnorm(g0 + h0*h[i] + g1*off[i] + g2*def[i],tau1)
  }
  
  for(i in 1:length(y)){
      log(off[i]) <- a0 + a1*a[i] + a2*b[i] + a3*c[i]+ a4*d[i] + a5*e[i] 
      log(def[i]) <- b0 + b1*f[i] + b2*g[i] + b3*j[i] + b4*k[i] + b5*l[i]
  }



  #Priors
  h0 ~ dnorm(3,1)
  g0 ~ dnorm(5,1/10)
  g1 ~ dnorm(5,1/10)
  g2 ~ dnorm(5,1/10)

  a0 ~ dnorm(5,1/10)
  a1 ~ dnorm(5,1/10)
  a2 ~ dnorm(5,1/10)
  a3 ~ dnorm(5,1/10)
  a4 ~ dnorm(5,1/10)
  a5 ~ dnorm(5,1/10)

  b0 ~ dnorm(5,1/10)
  b1 ~ dnorm(5,1/10)
  b2 ~ dnorm(5,1/10)
  b3 ~ dnorm(5,1/10)
  b4 ~ dnorm(5,1/10)
  b5 ~ dnorm(5,1/10)


  tau1 ~ dgamma(1,1/10)
}"


main1_jags <- jags.model(textConnection(main1), 
               data= list(y=modelData$`Offense Points`,a = modelData$O_Points,b=modelData$`O_Avg Rush`,c=modelData$`D_Avg Pass`,d=modelData$`O_Net Rush`,e = modelData$`O_Net Pass`,f = modelData$D_Points,g=modelData$`D_Avg Rush`,j=modelData$`D_Avg Pass`,k=modelData$`D_Net Rush`,l=modelData$`D_Net Pass`, h=modelData$`Is Home`),
                    inits=list(.RNG.name="base::Wichmann-Hill", .RNG.seed=1989))


main1_sim <- coda.samples(main1_jags, variable.names=c("h0","g0","g1","g2","a0","a1","a2","a3","a4","a5","b0","b1","b2","b3","b4","b5","tau1"), n.iter=10000)
   
main1_sample <- data.frame(step=1:10000, main1_sim[[1]])
head(main1_sample)
```
```{r}
summary(main1_sim)
plot(main1_sim)
```
```{r}
set.seed(1000)
predictmain1 <- function(a,b,c,d,e,f,g,j,k,l,h){
  offense <-  exp(main1_sample$a0 + main1_sample$a1*a + main1_sample$a2*b + main1_sample$a3*c + main1_sample$a4*d + main1_sample$a5*e)
  defense <- exp(main1_sample$b0 + main1_sample$b1*f + main1_sample$b2*g + main1_sample$b3*j + main1_sample$b4*k + main1_sample$b5*l)
  
  rate <- rnorm(main1_sample$g0 + main1_sample$h0*h + main1_sample$g1*offense + main1_sample$g2*defense, sqrt(1/main1_sample$tau1))
  rate[rate<0]<-0
  
  prediction <- rpois(10000,rate)
  return(prediction)
}
```
```{r}
modelData <- modelDF2016 %>% filter(Week>5) %>% arrange(Week)

superbowl <- modelData[nrow(modelData),]
# View(superbowl)
NE_prediction <-predictmain1(superbowl[,9],superbowl[,11],superbowl[,13],superbowl[,10],superbowl[,12],superbowl[,19],superbowl[,21],superbowl[,23],superbowl[,20],superbowl[,22],superbowl[,24])

head(NE_prediction)
mean(NE_prediction)

NE_prediction <- data.frame(NE_prediction)

colnames(NE_prediction)[1]<- "prediction"

ggplot(NE_prediction, aes(x=prediction)) + geom_histogram(aes(y=..density..))




```




```{r}
modelData <- modelDF2016 %>% filter(Week>5) %>% arrange(Week)

superbowl <- modelData[nrow(modelData),]
# View(superbowl)
NE_prediction <-predictmain1(superbowl[,9],superbowl[,11],superbowl[,13],superbowl[,10],superbowl[,12],superbowl[,19],superbowl[,21],superbowl[,23],superbowl[,20],superbowl[,22],superbowl[,24])

head(NE_prediction)
mean(NE_prediction)

NE_prediction <- data.frame(NE_prediction)

colnames(NE_prediction)[1]<- "prediction"

ggplot(NE_prediction, aes(x=prediction)) + geom_histogram(aes(y=..density..))



```
```{r}
set.seed(1000)
main_predict1 = data.frame(predictmain1(.5,.5,0))
colnames(main_predict1)[1]<- "prediction"

ggplot(main_predict1, aes(x=prediction)) + geom_histogram(aes(y=..density..))

```










```{r}
#Overspecified Model where offensive stats combine into an offensive score and likewise with defenseive stats


modelData <- filter(modelDF2016,Week>5)

main1 <- "model{
  #Data 
  for(i in 1:length(y)) {
      y[i] ~ dpois(rate[i])
      log(rate[i]) <- a0 + a1*(a[i]/(a[i]+f[i]))+a2*(b[i]/(b[i]+g[i]))+a3*(c[i]/(c[i]+j[i])) +a4*(d[i]/(d[i]+k[i])) + a5*(e[i]/(e[i]+l[i]))
  }
  


  #prior

  h0 ~ dnorm(3,1)
  a0 ~ dnorm(10,1/10)
  a1 ~ dnorm(10,1/10)
  a2 ~ dnorm(10,1/10)
  a3 ~ dnorm(10,1/10)
  a4 ~ dnorm(10,1/10)
  a5 ~ dnorm(10,1/10)

}"


main1_jags <- jags.model(textConnection(main1), 
               data= list(y=modelData$`Offense Points`,a = modelData$O_Points,b=modelData$`O_Avg Rush`,c=modelData$`D_Avg Pass`,d=modelData$`O_Net Rush`,e = modelData$`O_Net Pass`,f = modelData$D_Points,g=modelData$`D_Avg Rush`,j=modelData$`D_Avg Pass`,k=modelData$`D_Net Rush`,l=modelData$`D_Net Pass`, h=modelData$`Is Home`),
                    inits=list(.RNG.name="base::Wichmann-Hill", .RNG.seed=1989))


main1_sim <- coda.samples(main1_jags, variable.names=c("h0","a0","a1","a2","a3","a4","a5"), n.iter=10000)
   
main1_sample <- data.frame(step=1:10000, main1_sim[[1]])
head(main1_sample)
```
```{r}
summary(main1_sim)
plot(main1_sim)
```
```{r}
set.seed(1000)
predictmain1 <- function(a,b,c,d,e,f,g,j,k,l,h){
  rate <- main1_sample$a0 + main1_sample$h0*h + main1_sample$a1*(a/(a+f)) +main1_sample$a2*(b/(b+g)) + main1_sample$a3*(c/(c+j))+main1_sample$a4*(d/(d+k)) + main1_sample$a5*(e/(e+l))
  rate[rate<0]<-0
  
  prediction <- rpois(10000,rate)
  return(rate)
}
```
```{r}
modelData <- modelDF2016 %>% filter(Week>5) %>% arrange(Week)

superbowl <- modelData[nrow(modelData),]
# View(superbowl)
NE_prediction <-predictmain1(superbowl[,9],superbowl[,11],superbowl[,13],superbowl[,10],superbowl[,12],superbowl[,19],superbowl[,21],superbowl[,23],superbowl[,20],superbowl[,22],superbowl[,24])

head(NE_prediction)
mean(NE_prediction)
```


```{r}
modelData <- modelDF2016 %>% filter(Week>5) %>% arrange(Week)

superbowl <- modelData[nrow(modelData),]
# View(superbowl)
NE_prediction <-predictmain1(superbowl[,9],superbowl[,11],superbowl[,13],superbowl[,10],superbowl[,12],superbowl[,19],superbowl[,21],superbowl[,23],superbowl[,20],superbowl[,22],superbowl[,24])

head(NE_prediction)
mean(NE_prediction)

NE_prediction <- data.frame(NE_prediction)

colnames(NE_prediction)[1]<- "prediction"

ggplot(NE_prediction, aes(x=prediction)) + geom_histogram(aes(y=..density..))



```
```{r}
set.seed(1000)
main_predict1 = data.frame(predictmain1(.5,.5,0))
colnames(main_predict1)[1]<- "prediction"

ggplot(main_predict1, aes(x=prediction)) + geom_histogram(aes(y=..density..))

```


```{r}
#Overspecified Model where offensive stats combine into an offensive score and likewise with defenseive stats


modelData <- filter(modelDF2016,Week>5)

main1 <- "model{
  #Data 
  for(i in 1:length(y)) {
      y[i] ~ dpois(rate[i])
      rate[i] ~ dnorm(h0*h[i] + a0 + a1*(a[i]/(a[i]+f[i])),tau1) 
  }
  




  #Priors
  h0 ~ dnorm(3,1)
  
  a0 ~ dnorm(0,1/10)
  a1 ~ dnorm(10,1/10)

  tau1 ~ dgamma(1,1/10)
}"


main1_jags <- jags.model(textConnection(main1), 
               data= list(y=modelData$`Offense Points`,a = modelData$O_Points,f = modelData$D_Points, h=modelData$`Is Home`),
                    inits=list(.RNG.name="base::Wichmann-Hill", .RNG.seed=1989))


main1_sim <- coda.samples(main1_jags, variable.names=c("h0","a0","a1","tau1"), n.iter=10000)
   
main1_sample <- data.frame(step=1:10000, main1_sim[[1]])
head(main1_sample)
```
```{r}
summary(main1_sim)
plot(main1_sim)
```

```{r}
modelData <- modelDF2016 %>% filter(Week>5) %>% arrange(Week)

superbowl <- modelData[nrow(modelData),]
# View(superbowl)
NE_prediction <-predictmain1(superbowl[,9],superbowl[,11],superbowl[,13],superbowl[,10],superbowl[,12],superbowl[,19],superbowl[,21],superbowl[,23],superbowl[,20],superbowl[,22],superbowl[,24])

head(NE_prediction)
mean(NE_prediction)

NE_prediction <- data.frame(NE_prediction)

colnames(NE_prediction)[1]<- "prediction"

ggplot(NE_prediction, aes(x=prediction)) + geom_histogram(aes(y=..density..))



```









































































```{r}
modelData <- filter(modelDF2016,Week>5)


main1 <- "model{
  #Data 
  for(i in 1:length(y)) {

      y[i] ~ dpois(rate[i])
      
      rate[i] ~ dnorm(g0 +h0*h[i] + g1*off[i]+g2*def[i],tau)
  }
  
  for(j in 1:length(y)){
      off[j] <- a0 + a1*o1[j] + a2*o2[j] + a3*o3[j] + a4*o4[j] + a5*o5[j]
      def[j] <- b0 + b1*d1[j] + b2*d2[j] + b3*d3[j] + b4*d4[j] + b5*d5[j]
  }

  #Priors
  h0 ~ dnorm(3,1)
  g0 ~ dnorm(0,1/10)
  g1 ~ dnorm(10,1/10)
  g2 ~ dnorm(-10,1/10)

  a0 ~ dnorm(5,1/10)
  a1 ~ dnorm(5,1/10)
  a2 ~ dnorm(5,1/10)
  a3 ~ dnorm(5,1/10)
  a4 ~ dnorm(5,1/10)
  a5 ~ dnorm(5,1/10)
  
  b0 ~ dnorm(5,1/10)
  b1 ~ dnorm(5,1/10)
  b2 ~ dnorm(5,1/10)
  b3 ~ dnorm(5,1/10)
  b4 ~ dnorm(5,1/10)
  b5 ~ dnorm(5,1/10)

  tau ~ dgamma(100,10)
}"


main1_jags <- jags.model(textConnection(main1), 
               data= list(y=modelData$`Offense Points`,o1 = modelData$O_Points,o2=modelData$`O_Avg Rush`,o3=modelData$`O_Avg Pass`,o4=modelData$`O_Net Rush`,o5 = modelData$`O_Net Pass`,d1 = modelData$D_Points,d2 = modelData$`D_Avg Rush`,d3 = modelData$`D_Avg Pass`,d4=modelData$`D_Net Rush`,d5 = modelData$`D_Net Pass`, h=modelData$`Is Home`),
                    inits=list(.RNG.name="base::Wichmann-Hill", .RNG.seed=1989))


main1_sim <- coda.samples(main1_jags, variable.names=c("h0","g0","g1","g2","a0","a1","a2","a3","a4","a5","b0","b1","b2","b3","b4","b5","tau"), n.iter=10000)
   
main1_sample <- data.frame(step=1:10000, main1_sim[[1]])
head(main1_sample)
```
```{r}
summary(main1_sim)
```
```{r}
set.seed(1000)
predictmain1 <- function(x,w,h){
  prediction <- rpois(10000, main1_sample$b0 + main1_sample$b1*(x/(x+w)) + main1_sample$b10*h)
}

head(predictmain1(.5,.5,0))
mean(predictmain1(.5,.5,0))

mean(predictmain1(.5,.3,0))


```
```{r}
set.seed(1000)
main_predict1 = data.frame(predictmain1(.5,.5,0))
colnames(main_predict1)[1]<- "prediction"

ggplot(main_predict1, aes(x=prediction)) + geom_histogram(aes(y=..density..))

```






main2 <- "model{
  #Data 
  for(i in 1:length(y)) {
      y[i] ~ dpois(mu[i])
      log(mu[i]) <- b0 + b1*(o[i]/(o[i]+d[i])) +b2*(or[i]/(or[i]+dr[i])) +b3*(op[i]/(op[i]+dp[i])) + h0*h[i]
  }

  #Priors
  h0 ~ dnorm(3,1)

  b0 ~ dnorm(0,1/100)
  b1 ~ dnorm(0,1/100)
  b2 ~ dnorm(0,1/100)
  b3 ~ dnorm(0,1/100)

}"


main2_jags <- jags.model(textConnection(main2), 
               data= list(y=modelData$`Offense Points`, o=modelData$O_Points, d=modelData$D_Points,or = modelData$`O_Net Rush`,op = modelData$`O_Net Pass`,dr=modelData$`D_Net Rush`,dp = modelData$`D_Net Pass`, h=modelData$`Is Home`),
                    inits=list(.RNG.name="base::Wichmann-Hill", .RNG.seed=1989))


main2_sim <- coda.samples(main2_jags, variable.names=c("h0","b0","b1","b2","b3"), n.iter=10000)
   
main2_sample <- data.frame(step=1:10000, main2_sim[[1]])
head(main2_sample)

summary(main2_sim)
plot(main2_sim)

set.seed(13)
predictmain2 <- function(o,d,or,op,dr,dp,h){
  prediction <- rpois(10000,exp(main2_sample$b0 + main2_sample$b1*(o/(o+d)) +main2_sample$b1*(or/(or+dr))+main2_sample$b3*(op/(op+dp))+ main2_sample$h0*h))


comparePrediction2 <- function(scores,O_data,D_data,O_rush,O_pass,D_rush,D_pass,is_home){
  vals = rep(0,length(scores))
  for(i in 1:length(scores)){
    actualScore = scores[i]
    prediction = predictmain2(O_data[i],D_data[i],O_rush[i],O_pass[i],D_rush[i],D_pass[i],is_home[i])
    vals[i]=prediction - actualScore
  }
  return(vals)
}


set.seed(13)
modelData2016 <- filter(modelDF2016,Week>5)
predictionAccuracy = data.frame(comparePrediction2(modelData2016[,4],modelData2016[,9],modelData2016[,19],modelData2016[,10],modelData2016[,12],modelData2016[,20],modelData2016[,22],modelData2016[,24]))

colnames(predictionAccuracy)[1]<- "prediction"
ggplot(predictionAccuracy, aes(x=prediction)) + geom_histogram(binwidth = 3, aes(y=..density..))

# modelData2016 <- filter(modelDF2016,Week>5)
predictionAccuracy2 = data.frame(comparePrediction2(rep(0,nrow(modelData2016)),modelData2016[,9],modelData2016[,19],modelData2016[,10],modelData2016[,12],modelData2016[,20],modelData2016[,22],modelData2016[,24]))

colnames(predictionAccuracy2)[1]<- "prediction"
ggplot(predictionAccuracy2, aes(x=prediction)) + geom_histogram(binwidth = 3, aes(y=..density..))















